---
title: "Machine Learning for Biomarker Discovery"
author: "Laura Bravo Merodio"
output: 
  html_document:
    #theme: sandstone
    theme: lumen
    #code_folding: "hide"
    number_sections: TRUE
    toc: true
    toc_float:
        collapsed: true
        smooth_scroll: true
    toc_depth: 3
    fig_caption: yes
    code_folding: show

fontsize: 14pt
---

```{r setup, include=FALSE}

#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

```


# Introduction

This is a report that summarizes the main results from the research, including plots and tables. It is set so as to mimic the analysis pipeline undergone in the app.

***
***

# Data exploration 

Your data looks like this: 

```{r Desc, fig.height=10, fig.width=12}
plot1()
```

# Feature Selection


```{r plot3, fig.height=10, fig.width=10}

FeatSel2()

```

The chosen features are: 

```{r plot7, fig.height=10, fig.width=10}

KeyFeats() %>%
  #rename(" " = "x") %>%
  kbl(caption = "Selected Features") %>%
  kable_classic(full_width = F, html_font = "Cambria")
  #kable(., digits = 2, format.args = list(scientific = FALSE))


```

Given this ranking table 

```{r}

FinalFS2() %>%
  kbl(caption = "Selected Features") %>%
  kable_classic(full_width = F, html_font = "Cambria")
  #kable(., digits = 2, format.args = list(scientific = FALSE))

```


# Model building

Then model building with the selected parameters: Models: `r SelMods()` and Bootstraps: `r Boost()` of the following models 

```{r plot8, fig.height=10, fig.width=10}

Variables() %>%
  kbl(caption = "Variables") %>%
  kable_classic(full_width = F, html_font = "Cambria")
  #kable(., digits = 2, format.args = list(scientific = FALSE))

```

# Results

```{r plot2, fig.height=10, fig.width=10}

 FinalFinalPlot2()

```


```{r plot1, fig.height=5, fig.width=10}


FinalFinalPlot()


```


With top selected models being: 

```{r plot6, fig.height=10, fig.width=10}

q3A() %>%
  kbl(caption = "Selected Features") %>%
  kable_classic(full_width = F, html_font = "Cambria")
  #kable(., digits = 2, format.args = list(scientific = FALSE))

```


